A numerical study of the solution of X-Mode equations around the hybrid resonance

### 2015-04-22 report_clean/FD.tex
epsilon defined

\section{Frequency domain study}
In the frequency domain, the velocity can be eliminated and it yields a simpler system under the form
of  Maxwell equations with the cold plasma dielectric tensor \cite{Stix,Despres_2014}. One obtains the equations
\bealn
%\label{eq:main_frequency_domain_1}
\operatorname{curl}\operatorname{curl}\hat{\mathbf{E}}-
\epsilon(\omega)\hat{\mathbf{E}}=0,\\
\epsilon(\omega)=\left(
\begin{matrix}
 \tilde{\alpha} & i\tilde{\delta} \\
 -i\tilde{\delta}  & \tilde{\alpha}
\end{matrix}
\right),\\
\tilde{\alpha}(\omega,x)=\frac{\omega^2}{c^2}\left(1-\frac{\tilde{\omega}\omega_p^2}{\omega(\tilde{\omega}^2-\omega_c^2)}\right),\qquad 
\tilde{\delta}(\omega)=\frac{\omega_c\omega_p^2}{\omega(\tilde{\omega}^2-\omega_c^2)},
\eealn
where the frequency 
$\tilde{\omega}=\omega+i\nu$ is shifted in the complex plane,
the cyclotron frequency is 
$ \omega_c={\frac{eB_0}{m_e}}$ and the plasma frequency is $ \omega_p^2=\frac{e^2 N_e}{\epsilon_0 m_e}$.
The series expansion as $\nu\rightarrow 0$ gives at leading orders
\bealn
 \tilde{\alpha}(\omega,x)=\alpha(\omega,x)+i\nu\frac{\omega_p^2(\omega^2+\omega_c^2)}{(\omega^2-\omega_c^2)^2}\frac{\omega^2}{c^2},\qquad \alpha(\omega)=\frac{\omega^2}{c^2}\left(1-\frac{\omega_p^2}{\omega^2-\omega_c^2}\right),\\
 \tilde{\delta}(\omega)=\delta(\omega)-\frac{2i\omega^3\nu}{c^2(\omega^2-\omega_c^2)^2},\qquad \delta(\omega)=\frac{\omega\omega_c\omega_p^2}{c^2(\omega^2-\omega_c^2)}.
\eealn
We finally obtain a simpler equation \cite{Despres_2014} 
%\ben
% \epsilon_{\nu}(\omega)\approx \epsilon_0+i\nu Id,\; \nu\rightarrow 0.
%\een
%Thus, in this work we concentrate on a model
\begin{align}
\label{eq:main_frequency_domain}
\operatorname{curl}\operatorname{curl}\hat{\mathbf{E}}-\frac{\omega^2}{c^2}
\left(\epsilon_0(\omega)+\nu Id\right)\hat{\mathbf{E}}=0,\\
\label{eq:epsilon_0}
\epsilon_0(\omega)=\left(
\begin{matrix}
 \alpha & i\delta \\
 -i\delta & \alpha 
\end{matrix}
\right).
\end{align}
 In this model problem, the coefficients  $\alpha(\omega,x)$ and $\delta(\omega)$ are sufficiently smooth, i.e. bounded and continuous in  
$\left[-L,\; \mathbb{R}\right)$.

>>>>

\section{Frequency domain study}
In the frequency domain, the velocity can be eliminated and it yields a simpler system under the form
of  Maxwell equations with the cold plasma dielectric tensor \cite{Stix,Despres_2014}. One obtains the equations
\bealn
%\label{eq:main_frequency_domain_1}
\operatorname{curl}\operatorname{curl}\hat{\mathbf{E}}-
\epsilon(\omega)\hat{\mathbf{E}}=0,\\
\epsilon(\omega)=\left(
\begin{matrix}
 \tilde{\alpha} & i\tilde{\delta} \\
 -i\tilde{\delta}  & \tilde{\alpha}
\end{matrix}
\right),\\
\tilde{\alpha}(\omega,x)=\frac{\omega^2}{c^2}\left(1-\frac{\tilde{\omega}\omega_p^2}{\omega(\tilde{\omega}^2-\omega_c^2)}\right),\qquad 
\tilde{\delta}(\omega)=\frac{\omega_c\omega_p^2}{\omega(\tilde{\omega}^2-\omega_c^2)},
\eealn
where the frequency 
$\tilde{\omega}=\omega+i\nu$ is shifted in the complex plane,
the cyclotron frequency is 
$ \omega_c={\frac{eB_0}{m_e}}$ and the plasma frequency is $ \omega_p^2=\frac{e^2 N_e}{\epsilon_0 m_e}$,\textcolor{red}{and $\epsilon(\omega)$ is the dielectric tensor of the cold plasma approximation.}
The series expansion as $\nu\rightarrow 0$ gives at leading orders
\bealn
 \tilde{\alpha}(\omega,x)=\alpha(\omega,x)+i\nu\frac{\omega_p^2(\omega^2+\omega_c^2)}{(\omega^2-\omega_c^2)^2}\frac{\omega^2}{c^2},\qquad \alpha(\omega)=\frac{\omega^2}{c^2}\left(1-\frac{\omega_p^2}{\omega^2-\omega_c^2}\right),\\
 \tilde{\delta}(\omega)=\delta(\omega)-\frac{2i\omega^3\nu}{c^2(\omega^2-\omega_c^2)^2},\qquad \delta(\omega)=\frac{\omega\omega_c\omega_p^2}{c^2(\omega^2-\omega_c^2)}.
\eealn
We finally obtain a simpler equation \cite{Despres_2014} 
%\ben
% \epsilon_{\nu}(\omega)\approx \epsilon_0+i\nu Id,\; \nu\rightarrow 0.
%\een
%Thus, in this work we concentrate on a model
\begin{align}
\label{eq:main_frequency_domain}
\operatorname{curl}\operatorname{curl}\hat{\mathbf{E}}-\frac{\omega^2}{c^2}
\left(\epsilon_0(\omega)+\nu Id\right)\hat{\mathbf{E}}=0,\\
\label{eq:epsilon_0}
\epsilon_0(\omega)=\left(
\begin{matrix}
 \alpha & i\delta \\
 -i\delta & \alpha 
\end{matrix}
\right).
\end{align}
 In this model problem, the coefficients  $\alpha(\omega,x)$ and $\delta(\omega)$ are sufficiently smooth, i.e. bounded and continuous in  
$\left[-L,\; \mathbb{R}\right)$.
